---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# gpk

`gpk` contains the datasets from the [100 Datasets in Statistical Education](http://ces.iisc.ernet.in/hpg/nvjoshi/statspunedatabook/databook.html) project. These can be used for teaching statistics and R programming.

## Installation

You can install the stable version of gpk from CRAN with:

```{r cran-installation, eval = FALSE}
install.packages("gpk")
```

You can install the development version of gpk from github with:

```{r gh-installation, eval = FALSE}
# install.packages("devtools")
devtools::install_github("richierocks/gpk")
```

## Development work

The current development work aims to improve the documentation in the package,
making it easier to create lessons related to the data.

## Datasets

These datasets are available.

```{r example, echo = FALSE, results = "asis"}
knitr::kable(data(package = "gpk")$results[, c("Item", "Title")])
```
